Case for Support

### 2021-11-16 application/Je-S_sections.tex
Updates from Overleaf

To understand the brain, scientists aim to explain how animal behaviour relates to the activity in neural circuits. This necessitates design and precise control of behavioural experiments wherein experimental animals perform particular tasks while experimenters either record or manipulate neural activity in candidate neural circuits. Such experiments require data acquisition software that integrates and controls hardware from multiple recording devices (cameras, electrodes, sensors), and analysis tools that can interpret large and complex behavioural and neural datasets. Progress is held back by the lack of standardised tools for rapid design and implementation of experimental protocols, and the difficulty of integrating state-of-the-art data processing and neuroinformatics into custom experimental designs. The fields of behavioural and brain sciences have consequently suffered from both inefficiency and poor reproducibility, due to disparate data acquisition and analysis solutions created independently across laboratories.   
To address these challenges, we propose  to  extend,  enhance,  maintain  and  support \textbf{Bonsai},  a  fully  integrated  software  environment  to enable cutting-edge reproducible laboratory systems neuroscience experiments in animal models, with a particular emphasis on machine-intelligence-enabled, real-time neuroinformatics methods. While Bonsai is already adopted by hundreds of scientists worldwide to provide interactive experimental control, we aim to extend Bonsai’s functionality with a toolbox of online and offline Machine Intelligence tools for analysis of behavioural and neural data (video-based analysis of behavioural motifs, real-time and off-line analysis of neural signals), and create an open-access platform for software sharing and integration with multiple programming languages. These to the Bonsai ecosystem will enable new types of research, increase user base, and dramatically improve efficiency and reproducibility of research across behavioural and brain sciences.
[44 chars over]

>>>>

To understand the brain, scientists aim to explain how animal behaviour relates to the activity in neural circuits. This necessitates design and precise control of behavioural experiments wherein experimental animals perform particular tasks while experimenters either record or manipulate neural activity in candidate neural circuits. Such experiments require data acquisition software that integrates and controls hardware from multiple recording devices (cameras, electrodes, sensors), and analysis tools that can interpret large and complex behavioural and neural datasets. Progress is held back by the lack of standardised tools for rapid design and implementation of experimental protocols, and the difficulty of integrating state-of-the-art data processing and neuroinformatics into custom experimental designs. The fields of behavioural and brain sciences have consequently suffered from both inefficiency and poor reproducibility, due to disparate data acquisition and analysis solutions created independently across laboratories.   
To address these challenges, we propose  to  extend,  enhance,  maintain  and  support \textbf{Bonsai},  a  fully  integrated  software  environment  to enable cutting-edge reproducible laboratory systems neuroscience experiments in animal models, with a particular emphasis on machine-intelligence-enabled, real-time neuroinformatics methods. While Bonsai is already adopted by hundreds of scientists worldwide to provide interactive experimental control, we aim to extend Bonsai’s functionality with a toolbox of online and offline Machine Intelligence tools for analysis of behavioural and neural data (video-based analysis of behavioural motifs, real-time and off-line analysis of neural signals), and create an open-access platform for software sharing and integration with multiple programming languages. Enhancing Bonsai's ecosystem will enable new types of research, increase user base, and dramatically improve efficiency and reproducibility of research across behavioural and brain sciences.
[44 chars over]

### 2021-11-16 application/detailsOfResource.tex
Updates from Overleaf

We intend to improve an \textbf{existing resource}, the Bonsai ecosystem. We
propose to create software infrastructure to enable the\textbf{ integration of advanced data analysis methods} into
Bonsai (Section~\ref{sec:infrastructure}).
%
To demonstrate the use of this infrastructure, and to provide Bonsai users with
an initial set of advanced machine intelligence neural data analysis methods,
we will add to the Bonsai ecosystem machine learning functionality to control
neuroscience experiments and to analyse data generated by them
(Section~\ref{sec:functionality}).

>>>>

We intend to create software infrastructure to enable the\textbf{ integration of advanced data analysis methods} into
Bonsai (Section~\ref{sec:infrastructure}).
%
To demonstrate the use of this infrastructure, and to provide Bonsai users with
an initial set of advanced machine intelligence neural data analysis methods,
we will add to the Bonsai ecosystem machine learning functionality to control
neuroscience experiments and to analyse data generated by them
(Section~\ref{sec:functionality}).
